Page not found

### 2023-07-28 manuscript/chapters/2_neural_fields.qmd
whoopsie typooo

We should however note that the results obtained in @sec-fixedpoints are valid in the $N \to \infty$ limit. A numerical analysis shows in @fig-spectrum that at $N=250$, the numerical eigenvalues approximate the analytical eigenvalues, and this correspondence improves when we take larger $N$ (typically we will for the rest of this thesis take $N > 10^3$).

>>>>

We should however note that the results obtained in @sec-fixedpoints are valid in the $N \to \infty$ limit. A numerical analysis shows in @fig-spectrum that at $N=1024$, the numerical eigenvalues approximate the analytical eigenvalues, and this correspondence improves when we take larger $N$ (typically we will for the rest of this thesis take $N > 10^4$).
